Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-30 casestudies.tex
update case study and bib

The result of the dimensionality reduction is a two-dimensional plot
of the topic space, which can be seen in
Figure~\ref{fig:textvis}. Describe d3 view.

>>>>

The result of the dimensionality reduction process is a
two-dimensional plot of the topic space, which can be seen in
Figure~\ref{fig:textvis}. The interactive view is implemented with SVG
and Javascript through d3~\cite{Bostock:2011:DDD}. The most popular
web-based visualization libraries for R is ggvis~\cite{ggvis}, and so
a natural question becomes: could ggvis have been used instead of
custom Javascript?  In this case, the interactive features of ggvis
(and, by extension, Shiny) are a subset of those of Vega.  The custom
interactions in LDAVis (hovering over a single topic, hovering over a
topic cluster, hovering over a word in the distribution, etc) do not
appear to be available in the current version of Vega~\cite{vega},
although the required components for reactive interaction have been
recently described by Satyanarayan et
al.~\cite{Satyanarayan:2014:DID}. As a result, custom Javascript was
required in this case, making RCloud uniquely positioned among systems
available today.
